Multiparty Linear Regression via SPDZ

### 2017-06-14 paper/main.tex
formatting

\begin{figure}[h]
  \includegraphics[width=\linewidth]{results.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix A with d = 20. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality d. (Top) Fixed-point numbers with the b = 80 bits, with 60 in the fractional part. (Bottom) b = 41, with 28 in the fractional part}
  \label{fig:result1}
\end{figure}

@@

The run times for SPDZ are always comparable if not much faster. In terms of run-time, we observe that both Cholesky and LDLT were faster for smaller dimensions when d $\leq$ 100 and CGD is faster for larger dimensions when d > 100. This is consistent with the findings in the original experiment. For dimensions 100 and smaller, when Cholesky and LDLT are faster, they comparative differences are not that big (LDLT with 1.6 seconds compared to CGD 20 with 60.89 seconds) when compared to the largest differences between the larger sizes (LDLT with 1747 seconds and CGD5 with 97 seconds).

[insert table comparison here??]

In the condition number experiment, for CGD iterations of 5, 10, and 15, error increases as condition number increases. For example, in CGD 10 a small condition number may have an error of 10e-9 yet a larger condition number could have an error as large as 10e-3. However, in the CGD 20 case, the condition number does not seem to have as much of effect as the range of errors is much less., with the error varying only form 10e-11 to 10e-14 keeping in mind these are much smaller increments. (why?? Add some explanation about how condition number affects errors in a matrix) For the 60 bit precision case, we chose to run more iterations because in the CGD 20 line, there is a noticeable upward slope in the scatter plot, indicating that still as condition numbers increased, the errors were increasing as well. Indeed, 25 iterations showed some improvement as we can see a flatter trend in the points.

>>>>

\begin{figure}[h]
  \includegraphics[width=\linewidth]{results.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result1}
\end{figure}

@@

The run times for SPDZ are always comparable if not much faster. In terms of run-time, we observe that both Cholesky and LDLT were faster for smaller dimensions when $d \leq 100$ and CGD is faster for larger dimensions when $d > 100$. This is consistent with the findings in the original experiment. For dimensions 100 and smaller, when Cholesky and LDLT are faster, they comparative differences are not that big (LDLT with 1.6 seconds compared to CGD 20 with 60.89 seconds) when compared to the largest differences between the larger sizes (LDLT with 1747 seconds and CGD5 with 97 seconds).

\vc{insert table comparison here??}

In the condition number experiment, for CGD iterations of 5, 10, and 15, error increases as condition number increases. For example, in CGD 10 a small condition number may have an error of $\mathtt{10e-9}$ yet a larger condition number could have an error as large as $\mathtt{10e-3}$. However, in the CGD 20 case, the condition number does not seem to have as much of effect as the range of errors is much less., with the error varying only form $\mathtt{10e-11}$ to $\mathtt{10e-14}$ keeping in mind these are much smaller increments. \vc{why?? Add some explanation about how condition number affects errors in a matrix} For the 60 bit precision case, we chose to run more iterations because in the CGD 20 line, there is a noticeable upward slope in the scatter plot, indicating that still as condition numbers increased, the errors were increasing as well. Indeed, 25 iterations showed some improvement as we can see a flatter trend in the points.
